\documentclass[twocolumn]{article}

%% This is a convenience variable if you are using PGFPlots to build plots
%% within LaTeX. If you want to import PDF files for plots directly (and
%% not build them with TikZ in LaTeX), then comment the next line. To use
%% PDF files, they have to be in a `tikz' directory. To MAKE PDF files with
%% TikZ and PGFPlots, it is assumed that the texfile containing the source
%% are in a `tex' subdirectory relative to the directory which latex is run
%% in.
\newcommand{\makepdf}{}

%% Necessary LaTeX preambles to include for relevant functionality. We want
%% to start this file as fast as possible with the actual body of the
%% paper, while keeping modularity in the preambles.
\input{tex/pipeline.tex}
\input{tex/preamble-style.tex}
\input{tex/preamble-biblatex.tex}
\input{tex/preamble-pgfplots.tex}
\input{tex/preamble-necessary.tex}










%% Start writing.
\begin{document}

%% Write the title, authors and date.
\maketitle

%% -------- Delete this ---------
\section{Congratulations!}
Congratulations on running the reproduction pipeline! You can now follow
the checklist in the \texttt{README.md} file to customize this pipeline to
your exciting research project.

Just don't forget to \emph{never} use any numbers or fixed strings (for
example database urls like \url{\websurvey}) directly within your \LaTeX{}
source. Read them directly from your configuration files or outputs of the
programs as part of the reproduction pipeline and import them into \LaTeX{}
as macros through the \texttt{tex/pipeline.tex} file. See the several
examples within the pipeline for a demonstration. For some recent
real-world examples, the reproduction pipelines for Sections 4 and 7.3 of
\citet{bacon17} are available at
\href{https://doi.org/10.5281/zenodo.1164774}{zenodo.1164774}\footnote{\url{https://gitlab.com/makhlaghi/muse-udf-origin-only-hst-magnitudes}},
or
\href{https://doi.org/10.5281/zenodo.1163746}{zenodo.1163746}\footnote{\url{https://gitlab.com/makhlaghi/muse-udf-photometry-astrometry}}. Working
in this way, will let you focus clearly on your science and not have to
worry about fixing this or that number/name in the text.

Just as a demonstration of creating plots within \LaTeX{} (using the
PGFPlots package), in Figure \ref{deleteme} we show a plot of
\deletemenum{} random points that were generated by this pipeline using the
text manipulation program {\small AWK} (which is not the best random number
generator, but just used here to generate some values). The minimum value
in this distribution is $\deletememin$ and $\deletememax$ is the maximum.

The {\small PDF} file of Figure \ref{deleteme} is available in the
directory \texttt{\bdir/tex/build/tikz} and can be used in other contexts
(for example slides). If you want to directly use the PDF file in the
figure without having to let TiKZ decide if it should be remade or not, you
can also comment the \texttt{makepdf} macro at the top of this \LaTeX{}
source file.

PGFPlots is a great tool to build the plots within \LaTeX{} and removes the
necessity to add further dependencies (to create the plots) to your
reproduction pipeline. High-level language libraries like Matplotlib do
exist to also generate plots. However, bare in mind that they require many
dependencies (Python, Numpy and etc). Installing these dependencies from
source (after several years when the binaries are no longer available in
common repositories), is not easy and will harm the reproducibility of your
paper.

\begin{Figure}
  \includetikz{delete-me}

  \captionof{figure}{\label{deleteme} A random set of values plotted as a
    demonstration of how to generate plots within LaTeX.}
\end{Figure}

Furthermore, since PGFPlots is built by \LaTeX{} it respects all the
properties of your text (for example line width and fonts and etc), so the
final plot blends in your paper much more nicely. It also has a wonderful
manual\footnote{\url{http://mirrors.ctan.org/graphics/pgf/contrib/pgfplots/doc/pgfplots.pdf}}.


\section{Notice and citations}
To encourage other scientists to publish similarly reproducible papers,
please add a notice close to the start of your paper or in the end of the
abstract clearly mentioning that your work is fully reproducible.

For the time being, we haven't written a specific paper only for this
reproduction pipeline, so until then, we would be grateful if you could
cite the first paper that used the first version of this pipeline:
\citet{ai15}.

After publication, don't forget to upload all the necessary data, software
source code and the reproduction pipeline to a long-lasting host like
Zenodo (\url{https://zenodo.org/}).
%% ------------------------------



\printbibliography
\end{document}
